FinalManuscript_DISCS_UG

### 2019-04-04 pcsc-paper/parts/02_01_paillier.tex
Fix math typos

\subsubsection{Key Generation}
We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}\left(p-1,q-1\right)$.
We then define $L\left(x\right)$ to be the largest integer $v$ greater than zero such that $x-1 \geq vn$.
Then we select an integer $g$ such that $\gcd\left(L\left(g^\lambda \bmod n^2\right), n\right) = 1$ and $0\leq g \leq n^2$.
We denote the public key as $(g,n)$ and the private key $(p,q)$.
\subsubsection{Encryption and Decryption}
The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
\begin{equation*}
	E\left(m\right) = g^m \cdot r^n \mod{n^2},
\end{equation*}
where $r$ is a random non-negative integer less than $n^2$.
The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^*_{n^2}$ given a private key $(p,q)$ is defined as:
\begin{equation*}
	D\left(c\right) = L\left(c^\lambda \bmod n^2\right) \cdot \left(L\left(g^\lambda \bmod n^2\right)\right)^{-1} \mod n.
\end{equation*}
\subsubsection{Homomorphic Properties of the Paillier Cryptosystem}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively. They are defined as follows.

@@

Suppose Alice encrypts an integer $x$ and sends it so Bob has $E\left(x\right)$, and wants to obtain $E\left(x^2\right)$ without exposing the value of $x$.
\begin{itemize}
	\item Bob first selects a random integer $r$ and computes $E\left(x+r\right)$. Bob can do this since $r$ is a plaintext constant.
	\item Bob sends $E\left(x+r\right)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
	\item Alice squares $x+r$ and encrypts the result. She sends $E\left(\left(x+r\right)^2\right)$ to Bob.
	\item Bob computes $E\left(-2rx + r^2\right)$. He then computes
	\begin{align*}
		E\left(\left(x+r\right)^2\right)E\left(-2rx + r^2\right) = E\left(x^2\right).
	\end{align*}
\end{itemize}

\subsubsection{Secure Multiplication}
We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
Suppose Alice encrypts integers $x$ and $y$, and Bob has $E\left(x\right), E\left(y\right)$ and wants to obtain $E\left(xy\right)$.
\begin{itemize}
	\item Bob acquires $E\left(x^2\right)$ and $E\left(y^2\right)$ using the secure squaring protocol.
	\item Bob sends $E\left(x+y\right)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
	\item Alice sends $E\left(\left(x+y\right)^2\right)$ to Bob.
	\item Bob then computes
	\begin{align*}
		\frac{1}{2}E\left(\left(x+y\right)^2\right)E\left(x^2\right)^{-1}E\left(y^2\right)^{-1} &= \frac{1}{2}E\left(\left(x+y\right)^2 - x^2 - y^2\right)\\
		&= \frac{1}{2}E\left(2xy\right)\\
		&= E\left(xy\right).
	\end{align*}
\end{itemize}

>>>>

\subsubsection{Key Generation}
We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}\left(p-1,q-1\right)$.
We then define $L\left(x\right)$ to be the largest integer $v$ greater than zero such that $x-1 \geq vn$.
Then we select an integer $g$ such that $\gcd\left(L\left(g^\lambda \bmod n^2\right), n\right) = 1$ and $0\leq g \leq n^2$.
We denote the public key as $(g,n)$ and the private key $(p,q)$.
\subsubsection{Encryption and Decryption}
The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
\begin{equation*}
	E\left(m\right) = g^m \cdot r^n \mod{n^2},
\end{equation*}
where $r$ is a random non-negative integer less than $n^2$.
The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^*_{n^2}$ given a private key $(p,q)$ is defined as
\begin{equation*}
	D\left(c\right) = L\left(c^\lambda \bmod n^2\right) \cdot \left(L\left(g^\lambda \bmod n^2\right)\right)^{-1} \mod n,
\end{equation*}
where the function $L(x)$ is the largest integer $v$ greater than zero such that $x-1 \geq vn$.
\subsubsection{Homomorphic Properties of the Paillier Cryptosystem}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively. They are defined as follows.

@@

Suppose Alice encrypts an integer $x$ and sends it so Bob has $E\left(x\right)$, and wants to obtain $E\left(x^2\right)$ without exposing the value of $x$.
\begin{itemize}
	\item Bob first selects a random integer $r$ and computes $E\left(x+r\right)$. Bob can do this since $r$ is a plaintext constant.
	\item Bob sends $E\left(x+r\right)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
	\item Alice squares $x+r$ and encrypts, sending $E\left(\left(x+r\right)^2\right)$ to Bob.
	\item Bob then computes $E\left( \left(x+r\right)^2 + (-2rx + r^2)\right) = E\left(x^2\right)$.
\end{itemize}

\subsubsection{Secure Multiplication}
We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
Suppose Alice encrypts integers $x$ and $y$, and Bob has $E\left(x\right), E\left(y\right)$ and wants to obtain $E\left(xy\right)$.
\begin{itemize}
	\item Bob acquires $E\left(x^2\right)$ and $E\left(y^2\right)$ using the secure squaring protocol.
	\item Bob sends $E\left(x+y\right)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
	\item Alice sends $E\left(\left(x+y\right)^2\right)$ to Bob.
	\item Bob then computes $ E\left(\frac{1}{2} \left( \left(x+y\right)^2 - x^2 - y^2\right)\right) = E\left(xy\right)$.
\end{itemize}
